Collection of Visualization

### 2016-03-16 visualization/visualization.Rmd
visualization collection

---
title: "Collection of ggplot2 Plots"
date: "`r Sys.Date()`"
author: "Ming-Yu Liu"
output:
  rmdformats::readthedown:
    highlight: haddock
---

@@

<img src = "/Users/ethen/Business-Analytics/ggplot2/avoid_pie_charts/data_scientist.png" width = "400" height = "800" >

@@

library(scales)
library(ggplot2)
library(ggthemes)
library(data.table)
setwd("/Users/ethen/Business-Analytics/ggplot2/avoid_pie_charts")
d <- fread("pie.txt")
d <- melt( d, id.vars = "Task", 
		   variable.name = "Hours", value.name = "Percentage" )
head(d)

@@

>>>>

---
title: "Collection of Visualization"
date: "`r Sys.Date()`"
author: "Ming-Yu Liu"
output:
  rmdformats::readthedown:
    highlight: haddock
---

Articles related to producing informative visualization.

@@

<img src = "/Users/ethen/Business-Analytics/visualization/avoid_pie_charts/data_scientist.png" width = "400" height = "800" >

@@

library(scales)
library(ggplot2)
library(ggthemes)
library(data.table)
setwd("/Users/ethen/Business-Analytics/visualization/avoid_pie_charts")
d <- fread("pie.txt")
d <- melt( d, id.vars = "Task", 
		   variable.name = "Hours", value.name = "Percentage" )
head(d)

@@

**Sources:** source code can be obtained [here](https://github.com/ethen8181/Business-Analytics/blob/master/ggplot2/avoid_pie_charts/pie.R).
